%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Instructions for TSPL Exam
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{article}
\usepackage{a4,amssymb}
\usepackage{hyperref}

% \setlength{\oddsidemargin}{-1.5cm}
% \addtolength{\textwidth}{2cm}
% \addtolength{\textheight}{3cm}

\begin{document}
\pagestyle{empty}
\setcounter{page}{1}

\begin{center}
\Large Types and Semantics for Programming Languages \\
\LARGE Final Exam
\end{center}

\section*{Instructions}

\begin{itemize}

\item
  The exam lasts two hours.

\item
  Place your student identity card face-up on the desk in front of you.  The
  invigilator may come to check your identity, and in this case you may be asked
  to allow the invigilator to briefly use your computer.  The exam time has been
  calculated to allow time for such interruptions.

\item
  You are permitted to use your browser to access the following:
  \begin{quote}
    \url{plfa.inf.ed.ac.uk} -- the course textbook \\
    \url{agda.readthedocs.io/en/v2.6.3/} -- the Agda user manual
  \end{quote}
  You are also permitted to bring in two sides of A4 printed notes,
  covering whatever you find helpful. These may be inspected by the
  invigilator.

\item
  You are not permitted to bring in or access other materials during
  the exam. The only web pages you may browse during the exam are
  those above. The only files you may access are the file \texttt{Exam.lagda.md}
  and the parts of the standard library directly referenced by
  that file. The invigilator may see what materials you are accessing
  at any time.

\item
  Please ensure before submission that the file
  \texttt{Exam.lagda.md} contains your solutions to the exam.
  Submit using Gradescope as normal.

\item
  When the invigilators announce the end of the exam, you must
  submit and log out immediately.

\end{itemize}

\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
